---
title: "Resampling Methods"
author: "Yogesh Y Patil"
date: "`r Sys.Date()`"
output: html_document
---
1) Use the following different validation set approaches to estimate the test error rate by
fitting linear models to Auto data set. Consider mpg as response variable and
horsepower as predictor variable.
a) Use validation set approach by fitting polynomial regression of order 1 to 3. (Use
set.seed(1) and set.seed(2) function to get different results)
b) Use Leave-one-out Cross-validation (LOOCV) by fitting polynomial regression of
order 1 to 10.
c) Use k-fold Cross-validation by fitting polynomial regression of order 1 to 10 with k=5
and 10.
```{r}
library(ISLR2)
data(Auto)
set.seed(1)
train <- sample(392,196)
lm.fit <- lm(mpg~horsepower, data = Auto,subset = train)
mean((Auto$mpg-predict(lm.fit, Auto))[-train]^2)
lm.fit2 <-lm(mpg~poly(horsepower, 2), data = Auto,subset = train)
mean((Auto$mpg - predict(lm.fit2, Auto))[-train]^2)
lm.fit3 <- lm(mpg~poly(horsepower, 3), data = Auto,subset = train)
mean((Auto$mpg - predict(lm.fit3, Auto))[-train]^2)
```
```{r}
set.seed(2)
attach(Auto)
train <- sample(392,196)
lm.fit <- lm(mpg~horsepower, data = Auto,subset = train)
mean((mpg-predict(lm.fit, Auto))[-train]^2)
lm.fit2 <-lm(mpg~poly(horsepower, 2), data = Auto,subset = train)
mean((mpg - predict(lm.fit2, Auto))[-train]^2)
lm.fit3 <- lm(mpg~poly(horsepower, 3), data = Auto,subset = train)
mean((mpg - predict(lm.fit3, Auto))[-train]^2)
```
loocv
```{r}
library(boot)
glm.fit <- glm(mpg~horsepower,data=Auto)
cv.err <- cv.glm(Auto,glm.fit)
cv.err$delta
```
```{r}
cv.error <- rep(0,10)
for(i in 1:10){
  glm.fit <- glm(mpg~poly(horsepower,i),data=Auto)
cv.error[i] <- cv.glm(Auto,glm.fit)$delta[1]
}
cv.error

```
```{r}
set.seed(1)
cv.error.10 <- rep(0, 10)
for (i in 1:10) {glm.fit <- glm(mpg~poly(horsepower, i), data = Auto)
cv.error.10[i] <- cv.glm(Auto, glm.fit, K = 10)$delta[1]
}
cv.error.10
```
```{r}
set.seed(1)
cv.error.5 <- rep(0, 5)
for (i in 1:5) {glm.fit <- glm(mpg~poly(horsepower, i), data = Auto)
cv.error.5[i] <- cv.glm(Auto, glm.fit, K = 5)$delta[1]
}
cv.error.5

```
```{r}
library(ISLR2)
data("Portfolio")
alpha.fn <- function(data,index){X <- data$X[index]
Y <- data$Y[index]
(var(Y)-cov(X,Y))/(var(X)+var(Y)-2*cov(X,Y))
}
```
```{r}
alpha.fn(Portfolio,1:100)
```
```{r}
set.seed(7)
alpha.fn(Portfolio,sample(100,100))
```
```{r}
boot_ <- boot(Portfolio,alpha.fn,R=1000)
names(boot_)
help(boot)
plot(boot_)
hist(boot_$t)
```

```{r}
library(ISLR2)
data("Boston")
attach(Boston)
#a)
mu_hat <- mean(medv)
cat('The estimate for population mean is',mu_hat )
#b)
se_mu_hat <- sd(medv)/length(medv)
cat('\nThe estimate for se of mu_hat is',se_mu_hat )
#c)
boot.fn <- function(data,index){
  x <- data$medv[index]
  mu_hat2 <- mean(x)
  return(mu_hat2)
}
set.seed(1)
library(boot)
boot_ <- boot(Boston,boot.fn,1000)
hist(boot_$t)
plot(boot_)
```
```{r}
#d)
LL <- mu_hat-1.96*0.4106622
UL <- mu_hat+1.96*0.4106622
cat('95$ boostrap CI for population mean of medv is',c(LL,UL),'\n')

```
```{r}
t.test(medv)
cat('95 CI for population mean of medv using t.test',c(21.72953,23.33608),'\n')

```
E
```{r}
med.medv <- median(medv)
cat('The estimate for population median is',med.medv )

```
```{r}
rm(list=ls())
#f)
boot.fn <- function(data,index){
  x <- data$medv[index]
  mu_hat_median <- median(x)
  return(mu_hat_median)
}
set.seed(1)
library(boot)
boot_ <- boot(Boston,boot.fn,1000)
hist(boot_$t)
plot(boot_)
LL <- med.medv-1.96*0.3778075
UL <- med.medv+1.96*0.3778075
cat('95 CI for population median of medv using t.test',c(21.72953,23.33608),'\n')

```
```{r}
x=0;med=0
for (i in 1:1000) {
  x <- sample(medv,replace=T)
  med[i] <- median(x)
}

boostrap_median <- mean(med)
boostrap_se_median <- sd(med);boostrap_se_median
quantile(med,probs=c(0.025,0.975))

```
G
```{r}
boot.fn <- function(data,index){
  x <- data$medv[index]
  mu_0.1 <- quantile(x,0.1)
  return(mu_0.1)
}
set.seed(1)
library(boot)
boot_ <- boot(Boston,boot.fn,1000)
boot_
```
#Question 3
a)
```{r}
attach(Default)
lr.fit <- glm(default~income+balance,data=Default,family='binomial')
summary(lr.fit)$coefficients[2:3,2]
```
b)
```{r}
boot.fn <- function(data,index){
  default <- data$default[index]
  income <- data$income[index]
  balance <- data$balance[index]
  lm.fit <- glm(default~income+balance,data=Default,family=binomial)
  return(summary(lm.fit)$coefficients[2:3,1])
}
library(boot)
b=boot(Default,boot.fn,1000)
plot(b)
```

